---
title: Response to Meta-Analysis on Privacy Concerns and Information Sharing
subtitle: Supplementary Analyses
author: Tobias Dienlin & Ye Sun
ouput: html_document
---

```{r setup, echo=T, message=F, warning=F}
library(haven); library(lavaan); library(lavaanPlot); library(magrittr); library(tidyverse)
```

# Data Wrangling

We first load the data from Dienlin & Trepte (2015). 

```{r}
d <- read_spss("data.sav")
```

We build the following four mean-indices:

- pri_con: Privacy Concerns
- pri_att: Privacy Attitudes (analogous to privacy risk perception)
- pri_int: Privacy Intentions
- pri_beh: Privacy Behavior

```{r}
d %<>%
  mutate(
    pri_con = rowMeans(select(., starts_with("PB"))),
    pri_att = rowMeans(select(., starts_with("IN_EIN"))),
    pri_int = rowMeans(select(., starts_with("IN_INT"))),
    pri_beh = rowMeans(select(., starts_with("IN_VEA")))
  )
```

# Model Reported in Paper

We then configure a model similar to the one reported by Yu et al. (2020).

```{r}
model <- "
  pri_con ~~ pri_att
  pri_int ~ pri_con + pri_att
  pri_beh ~ pri_att + pri_int
"
fit_reported <- sem(model, d)
```

This model shows the following fit: 

```{r}
fitMeasures(fit_reported, c("chisq", "df", "pvalue", "cfi", "rmsea"))
```

Because one path (i.e., privacy concerns on privacy behavior) is not included (i.e., it is restricted to zero), model fit is slightly reduced.

# Saturated Model

We now fit a saturated model, which includes all paths.

```{r}
model <- "
  pri_con ~~ pri_att
  pri_int ~ pri_con + pri_att
  pri_beh ~ pri_con + pri_att + pri_int
"
fit_saturated <- sem(model, d)
```

This model shows the following fit: 

```{r}
fitMeasures(fit_saturated, c("chisq", "df", "pvalue", "cfi", "rmsea"))
```

Because the model is saturated, there are no degrees of freedom, and RMSEA equals zero.